---
title: "Mating_Topillos_Behavior"
author: "Fernanda"
date: "10/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Análisis Conductual

Cargar libraries

```{r}
library(dplyr)
#library(ggpubr)
library(tidyr)
library(ggplot2)
```

Cargar datos

```{r}
library(readxl)
Mating_topillos_behavior_dataframe <- read_excel("Mating_topillos_behavior_dataframe.xlsx")
#View(Mating_topillos_behavior_dataframe)
```

Fijar variables pareja

```{r}
Mating_topillos_behavior_dataframe %>%
  select(Sex, Percent_partner) -> partner_b

partner_b %>%
  filter(Sex == "F") -> partner_fem

partner_b %>%
  filter(Sex == "M") -> partner_mal

partner <- partner_b$Percent_partner

```

Fijar variables extraño

```{r}
Mating_topillos_behavior_dataframe %>%
  select(Sex, Percent_stranger) -> stranger_b

stranger_b %>%
  filter(Sex == "F") -> stranger_fem

stranger_b %>%
  filter(Sex == "M") -> stranger_mal

stranger <- stranger_b$Percent_stranger
```

Test de normalidad

```{r}
ggdensity(Mating_topillos_behavior_dataframe$Percent_partner, 
          main = "Density Percent Partner",
          xlab = "preference")
shapiro.test(Mating_topillos_behavior_dataframe$Percent_partner)

ggdensity(Mating_topillos_behavior_dataframe$Percent_stranger, 
          main = "Density Percent Stranger",
          xlab = "preference")
shapiro.test(Mating_topillos_behavior_dataframe$Percent_stranger)
```
Test de Wilcoxon

```{r}
wilcox.test(partner, stranger, alternative ="greater")

```
Grafica

```{r}
ggplot(Mating_topillos_behavior_dataframe, aes(x=percent)) 
```

#Calculo de datos estadísticos para Social Time

```{r}
library(readxl)
Behavior <- read_excel("Mating_topillos_behavior_dataframe.xlsx")
summary(Behavior$Percent_Socialtime)
std <- function(x) sd(x)/sqrt(length(x))
std(Behavior$Percent_Socialtime)
```

#Correlación entre Social Time y Preferencia de pareja

```{r}
#test de normalidad
shapiro.test(Behavior$Percent_Socialtime)
```
#Test de correlacion
```{r}
socialtimevspref_corr <- cor.test(Behavior$Percent_Socialtime, Behavior$PrefIndex, method= "spearman")

Behavior %>%
ggplot(data = Behavior, mapping = aes(x = Percent_Socialtime, y = PrefIndex)) +
    geom_smooth(method="lm", color = "pink", fill = scales::alpha("pink", alpha = 0.3), size = 1) +
    geom_point(mapping = aes(color = Sex), size = 2.5) + 
    xlim(20, 100) +
    ylim(0.0, 1.0) +
    scale_color_manual(values=c("deeppink3", "darkcyan")) +
    ggtitle("Relationship between Partner preference Index and Social Interaction") +
  xlab("\nPercentage of time on social incentive areas") + ylab("Partner preference Index\n") +
   theme(axis.text.y=element_text(size=12, hjust=0.2), axis.text.x=element_text(size=12, hjust=0.95)) +
    #annotate("text", x = 0.7*max(Acc_nacc$FC), y = 0.9*max(hud_lat_s01$Huddling_lat)) +
             #label = paste0("r(",cortext$parameter,")=",round(cortext$estimate,3))) +
    #theme_set(hud_theme)
    theme_classic()

  ggsave(filename = paste0("corr_","SocTimevsIndPref",".svg"), width = 5, height = 4)
```

# Huddling correlaction social time

```{r}
socialtimevshuddling_corr <- cor.test(Behavior$Percent_Socialtime, Behavior$Huddling_lat, method= "spearman")

Behavior %>%
ggplot(data = Behavior, mapping = aes(x = Percent_Socialtime, y = Huddling_lat)) +
    geom_smooth(method="lm", color = "plum3", fill = scales::alpha("plum3", alpha = 0.3)) +
    geom_point(mapping = aes(color = Sex), size = 2.5) + 
    scale_color_manual(values=c("deeppink3", "darkcyan")) +
    #xlab("Functional connectivity") + ylab("Huddling latency (min)") +
    ggtitle("Relationship between Huddling latency and Social interaction") +
   xlab("\nPercentage of time on social incentive areas") + ylab("Huddling latency (min)\n") +
  theme(axis.text.y=element_text(size=12, hjust=0.2), axis.text.x=element_text(size=12, hjust=0.95)) +
    #annotate("text", x = 0.7*max(Acc_nacc$FC), y = 0.9*max(hud_lat_s01$Huddling_lat)) +
             #label = paste0("r(",cortext$parameter,")=",round(cortext$estimate,3))) +
    #theme_set(hud_theme)
    theme_classic()

ggsave(filename = paste0("corr_","SocTimevsHuddling",".svg"), width = 5, height = 4)
```

# Huddling correlation partner pref

```{r}
prefindxvshuddling_corr <- cor.test(Behavior$PrefIndex, Behavior$Huddling_lat, method= "spearman")

Behavior %>%
ggplot(data = Behavior, mapping = aes(x = Huddling_lat, y = PrefIndex)) +
    geom_smooth(method="lm", color = "coral", fill = scales::alpha("coral", alpha = 0.3)) +
    geom_point(mapping = aes(color = Sex), size = 2.5) + 
    scale_color_manual(values=c("deeppink3", "darkcyan")) +
    #xlab("Functional connectivity") + ylab("Huddling latency (min)") +
    ggtitle("Relationship between Huddling latency and Partner preference Index") +
  xlab("\nHuddling Latency (min)") + ylab("Partner preference Index\n") +
  theme(axis.text.y=element_text(size=12, hjust=0.2), axis.text.x=element_text(size=12, hjust=0.95)) +
    #annotate("text", x = 0.7*max(Acc_nacc$FC), y = 0.9*max(hud_lat_s01$Huddling_lat)) +
             #label = paste0("r(",cortext$parameter,")=",round(cortext$estimate,3))) +
    #theme_set(hud_theme)
    theme_classic()

ggsave(filename = paste0("corr_","PrefIndxvsHuddling",".svg"), width = 5, height = 4)
```

# Male vs Female partner preference Index

```{r}

#dataframe_ppt_malevsfemale <- read_csv("Library/Mobile Documents/com~apple~CloudDocs/Topillos/Datos_Maestria/R_MT/Mating_Topillos/dataframe_ppt_malevsfemale.csv")

preffemvsmale <- cor.test(dataframe_ppt_malevsfemale$Male, dataframe_ppt_malevsfemale$Female, method= "spearman")

Behavior %>%
ggplot(data = dataframe_ppt_malevsfemale, mapping = aes(x = Male, y = Female)) +
    geom_smooth(method="lm", color = "lightblue2", fill = scales::alpha("lightblue2", alpha = 0.3)) +
    geom_point(size = 3, color = "royalblue4") + 
    #xlab("Functional connectivity") + ylab("Huddling latency (min)") +
    ggtitle("Relationship between Male and Female Partner preference Index") +
  xlab("\nMale Partner preference Index") + ylab("Female Partner preference Index\n") +
  theme(axis.text.y=element_text(size=12, hjust=0.2), axis.text.x=element_text(size=12, hjust=0.95)) +
    #annotate("text", x = 0.7*max(Acc_nacc$FC), y = 0.9*max(hud_lat_s01$Huddling_lat)) +
             #label = paste0("r(",cortext$parameter,")=",round(cortext$estimate,3))) +
    #theme_set(hud_theme)
    theme_classic()

ggsave(filename = paste0("corr_","PrefMalevsFemale",".svg"), width = 5, height = 4)
```


